---
title: "Developing Data Products Course Project"
author: "Kris Neuhalfen"
date: "12/12/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
currentwd <- getwd()
setwd(currentwd)

```
<style type="text/css">
body p {
  color: #000000;
}
</style>

<style type="text/css">
h1 p {
  color: #000000;
}
</style>

## Introduction

This presentation is part of the Developing Data Products Coursera.org course project submission.

It is an ioslides presentation generated with RStudio.

The Shiny application pitched by this presentation is at https://neuhalfen.shinyapps.io/DevelopingDataProducts/.

The Shiny app source code is available at https://github.com/jkneuf/DevelopingDataProducts.

## What is the purpose of the Shiny app?

- This Shiny application allows a user to analyze banks that offer four different financial products: FBB, FSR, SIMO, and TNMCS. 

- You can see the revenue generated by each bank in four selected regions of the country: East, North, South, and West.

- In addition, you can see how each financial product performs in each of the four regions of the country.





## How the Shiny app works

```{r screenshot, fig.width=8, fig.height=5, echo=FALSE}
library(png)
library(grid)
img <- readPNG("app_screenshot.PNG")
 grid.raster(img)

```

## Ready to give it a try?

Use the Shiny app at https://neuhalfen.shinyapps.io/DevelopingDataProducts/

Get the app source code at https://github.com/jkneuf/DevelopingDataProducts

The following code was used to display the screenshot of the Shiny app.

```{r code, eval=FALSE, echo=TRUE}
library(png)
library(grid)
img <- readPNG("app_screenshot.PNG")
 grid.raster(img)
```


